Improving reproducibility of scientific software using Nix/NixOS: A case study on preCICE adapters and solvers

### 2024-04-20 paper/paper.tex
feat(paper): Add note about success of the case study

In conclusion, the case study has shown that packaging of scientific software isn't as trivial as expected.
The majority of the packages required some solution for a fundamental issue within the scientific software or its build system that isn't solvable for none experienced Nix users, which makes it hard for people to use it even for their own software.
Nix itself also is partly at fault, because of its unique nature, that every piece of software lies within \texttt{/nix/store} and that each store path is its own-isolated tree based on the Filesystem Hierarchy Standard (FHS).
But it is worth mentioning that not only Nix would benefit from more streamlined build systems and packaging, because both Spack and EasyBuild do something similar for their packages, where each package also lies in its own FHS.
The work of the xSDK people and their policy might be a step in the right direction but looking at the current list of software that is available within the latest xSDK release, 26 libraries, indicates that it is an uphill battle that might take several more years, especially if we consider that the first release happened in 2016.
We have also seen, that the current HPC solutions, Spack and EasyBuild make it somewhat possible to reproducibly build software but not to the degree in which Nix allows it.
That is because they focus on flexibility of installing packages.
Spacks way of allowing users to change the compiler of a package, easily enable additional features on installation, override cflags and more advanced features, for example regarding mpi, shows that the Nix tooling needs more work or a layer on top that strips away the uniqueness of the DSL for something more user- and beginner-friendly.

>>>>

In conclusion, the case study was a success, as it has shown that packaging of scientific software with Nix is possible, but it isn't as trivial as expected.
Once the software is packaged, it is quite easy to be used and combined in environments with other packaged softwares without conflicts.
The packaged adapters and solvers work well together with the preCICE library and simulations can be run successfully, so this specific case study has shown the potential of Nix in the domain of scientific software.
More research has to be done on the topic, yet we are positive about possible future results in Nix abilities and its flexibility in similar domains.

The majority of the packages required some solution for a fundamental issue within the scientific software or its build system that isn't solvable for none experienced Nix users, which makes it hard for people to use it even for their own software.
Nix itself also is partly at fault, because of its unique nature, that every piece of software lies within \texttt{/nix/store} and that each store path is its own-isolated tree based on the Filesystem Hierarchy Standard (FHS).
But it is worth mentioning that not only Nix would benefit from more streamlined build systems and packaging, because both Spack and EasyBuild do something similar for their packages, where each package also lies in its own FHS.
The work of the xSDK people and their policy might be a step in the right direction but looking at the current list of software that is available within the latest xSDK release, 26 libraries, indicates that it is an uphill battle that might take several more years, especially if we consider that the first release happened in 2016.
We have also seen, that the current HPC solutions, Spack and EasyBuild make it somewhat possible to reproducibly build software but not to the degree in which Nix allows it.
That is because they focus on flexibility of installing packages.
Spacks way of allowing users to change the compiler of a package, easily enable additional features on installation, override cflags and more advanced features, for example regarding mpi, shows that the Nix tooling needs more work or a layer on top that strips away the uniqueness of the DSL for something more user- and beginner-friendly.
